### 2021-04-23 input/proposal.tex
mostly about implem

As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
not only requires eventual purging of stale control information, but
also the retrieval of the best up-to-date partitions. In that regard,
both kinds of $\delta$ messages have dual use: since they already
reach the borders of their partition when they remove stale control
information, they also trigger a competition when reaching such
bordering \processes (see Line~\ref{line:ascast_compete}). This simply
consists in sending the current partition through the communication
link from which the \process received the $\delta$. Upon receipt of
this answer, \processes act normally by propagating their changes when
they improve. \TODO{Exemple with figure for detection?}

\TODO{Rework this.}\NAME guarantees dynamic consistent partitioning by
making extensive use of \process to \process communications. In terms
of number of messages, in the average-case, a \process $i$ chosen
uniformly at random among all \processes creates a logical
partition. Its messages $\alpha_i$ propagate through the network until
reaching \processes that belong to another partition closer to
them. This splits partitions in half in average. Overall, the $a^{th}$
new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
      \log_2 a \rfloor}})$} \processes. This decreases every new
partition until reaching $0$ \processes per new partition: even the
chosen \process already belongs to its optimal partition. The average
number of messages per \process is
\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}. \TODO{Multiple receipt and multiple delivery imply
  more messages (receipt bounded by $|O|$ as well).} Deleting the
$a^{th}$ partition generates the exact same number of messages than
the $a^{th}$ partition creation. \TODO{But what about echos?} In the
worst-case, every new partition includes all but one \process
belonging to the previous partition. The total number of messages
after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
a^2)$. As for the average-case, the number of messages for the
partition deletion is identical to the number of messages of the
corresponding partition creation.

@@

Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. Removing an edge between two
\processes may invalidate the shortest path of one of involved
\processes plus downstream \processes. To implement this behavior,
\NAME uses the implementation of $\delta?$ messages. This prove costly
but enables \NAME even in dynamic networks subject to physical
partitioning.

>>>>

As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
not only requires eventual purging of stale control information, but
also the retrieval of the best up-to-date partitions. In that regard,
both kinds of $\delta$ messages have dual use: since they already
reach the borders of their partition when they remove stale control
information, they also trigger a competition when reaching such
bordering \processes (see Line~\ref{line:ascast_compete}). This simply
consists in sending the current partition through the communication
link from which the \process received the $\delta$. Upon receipt of
this answer, \processes act normally by propagating their changes when
they improve.

\NAME guarantees dynamic consistent partitioning by making extensive
use of \process-to-\process communications. It requires
\begin{inparaenum}[(i)]
\item purging stale control information, hence propagating $\delta$
  messages; and
\item retrieving the closest source, hence propagating $\alpha$
  messages.
\end{inparaenum}
In terms of number of messages, in the average-case, a \process $i$
chosen uniformly at random among all \processes creates a logical
partition. Its messages $\alpha_i$ propagate through the network until
reaching \processes that belong to another partition closer to
them. This splits partitions in half in average. Overall, the $a^{th}$
new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
      \log_2 a \rfloor}})$} \processes. This decreases every new
partition until reaching one \process per new partition: its
source. The average number of messages per \process is
\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
number of neighbors per \process. % \TODO{Multiple receipt and multiple
%  delivery imply more messages (receipt bounded by $|O|$ as well).}
Deleting the $a^{th}$ partition generates twice as many messages as
creating the $a^{th}$ partition: $\delta$ messages travel through the
partition, then $\alpha$ messages compete to fill the gap.  Overall,
the communication complexity shows that \NAME scales well to the
number of partitions.
%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.

@@

Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes only. If one or the other \process
improves, the propagation of $\alpha$ messages operates normally.
Removing an edge between two \processes may invalidate the shortest
path of one of involved \processes plus downstream \processes. As a
side effect, removing an edge may also impair the propagation of a
partition delete. To implement this behavior, \NAME uses its
implementation of $\delta?$ messages. This prove costly but
enables \NAME even in dynamic networks subject to physical
partitioning.

Next Section provides the details of our experimentation that aim to
evaluate the proposed implementation of logical dynamic partitioning
in dynamic networks.
